Using best practices for forecasting biodiversity changes in breeding birds

### 2017-08-02 manuscript/draft.Rmd
More changes.

The site-observer model found that 70% of the variance in richness in the
training set could be explained by differences among sites, and 21% could be
explained by differences among observers. The remaining 9% represents residual
variation, where a given observer might report a different number of species in
different years. In the training set, the residuals had a standard deviation of
about `r numbers$resid_sd` species. After correcting for observer differences,
there was little temporal autocorrelation in these residuals ([[about 0.04, +/-
something]]), suggesting that richness is approximately stationary on these time
scales.

>>>>

The site-observer mixed model found that 70% of the variance in richness in the
training set could be explained by differences among sites, and 21% could be
explained by differences among observers. The remaining 9% represents residual
variation, where a given observer might report a different number of species in
different years. In the training set, the residuals had a standard deviation of
about `r numbers$resid_sd` species. After correcting for observer differences,
there was little temporal autocorrelation in these residuals (i.e. the residuals
in one year explain `r round(100 *numbers$residual_autocor^2, 1)`% of the
variance in the residuals of the following year), suggesting that richness was
approximately stationary between 1982 and 2003.
